{\fontfamily{ptm}\selectfont Inexect Accelerated Proximal Gradient }

### 2025-09-22 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes a lot

@@

\title{{\fontfamily{ptm}\selectfont An Inexact Accelreated Proximal Gradient Method for TV Variation Problems}}

\date{\today}

\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
% \vskip 8mm

\begin{abstract} 
    \noindent
    Not yet added. 
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

% ==============================================================================
\section{Introduction}
    Let's make a type of algorithm that has the niche for applications with a state of the art performance. 
    \begin{assumption}\label{ass:smooth-nsmooth-sum}
        We assume the following about $(F, f, g, L, X^+)$: 
        \begin{enumerate}[nosep]
            \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function but doesn't support simple implementations of its proximal operator. 
            \item $g: \RR^n \rightarrow \RR$ is convex, proper, and closed, and its proximal operator can be easily implemented, and easy to obtain some element $\partial g$ at all points of the domain. 
            \item The over all objective has $F = f + g$. 
        \end{enumerate}
        Under this assumption, we denote the proximal gradient operator of $F = f+ g$ as $T_B(x) = \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x))$. 
        Note that by definition it has also:
        \begin{align*}
            T_B(x) &= 
            \hprox_{B^{-1}g}\left(
                x - B^{-1}\nabla f(x)
            \right)
            \\
            &= \argmin_{z}\left\lbrace
                g(z)
                + \langle \nabla f(x), z\rangle
                + \frac{B}{2}\Vert z - x \Vert^2
            \right\rbrace. 
        \end{align*}
    \end{assumption}
    \begin{definition}[A measure of error from proximal gradient evaluations]\;\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}. 
        For all $x, z \in \RR^n$, define $S$: 
        \begin{align*}
            S_B(z | x) &= \partial 
            \left[
                z \mapsto g(z)
                + \langle \nabla f(x), z\rangle
                + \frac{B}{2}\Vert z - x \Vert^2
            \right](z). 
        \end{align*}
    \end{definition}
    Observe: 
    \begin{enumerate}[nosep]
        \item $S_B(z | x) = \partial g(z) + \nabla f(x)+ B(z - x)$,
        \item $\mathbf 0 \in S_B(T(x) | x)$, 
        \item $(S_B(\cdot | x))^{-1}(\mathbf 0)$ is a singleton by strong convexity. 
    \end{enumerate}
    Let's assume inexact evaluation of $\tilde x \approx T_B(x)$, then the error measure is the set $S_B(\tilde x | x)$. 
    Assuming that we have accurate information on $\nabla f(x)$, then $\forall w \in S_B(\tilde x | x)\;\exists \tilde v \in \partial g(\tilde x)$. 
    \begin{align*}
        w &= \tilde v + \nabla f(x) + B(\tilde x - x). 
    \end{align*}
    We want to control $w$ in the implementations of inexact accelerated proximal gradient algorithm.

\section{Key ideas we need to get right}
    \begin{definition}[inexact proximal gradient]\;\label{def:inxt-pg}\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
        We Define for all $x \in \RR^n$ the inexact proximal gradient operator $T_B^{(\epsilon)}(x)$ to be such that if $\tilde x \in T^{(\epsilon)}_{B}(x)$ then, $\exists w \in S_{B}(\tilde x | x):\Vert w\Vert\le \epsilon \Vert \tilde x - x\Vert$.         

@@

    The algorithm we will design must produce iterates in a way that satisfies the inexact proximal gradient operator define above. 
    The following theorem will characterize a key inequality for convergence claim. 
    \begin{theorem}[inexact over regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum}.
        Take $T^{(\epsilon)}_B$ as given in Definition \ref{def:inxt-pg}. 
        For all $x\in \RR^n$, if $\exists B \ge 0$ such that $\tilde x \in T_{B + \epsilon}^{(\epsilon)}(x)$ and, $D_f(\tilde x, x)\le \frac{B}{2}\Vert \tilde x - x\Vert^2$. 
        Then for all $z, x \in \RR^n$ it has: 

@@

            0 &\le F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 

@@

        By Definition \ref{def:inxt-pg}, $T_{B + \epsilon}^{(\epsilon)}(x)$ minimizes a $h(z) = z \mapsto g(z) + \langle \nabla f(x), z \rangle + \frac{B + \epsilon}{2}\Vert x - z\Vert^2$ to produce $\tilde x$ so that $w \in S_{B + \epsilon}(\tilde x| x) = \partial h(x)$. 
        $h$ is $B + \epsilon$ strongly convex by convexity of $g$. 
        Since $w \in \partial h(\tilde x)$, it has subgradient inequality through strong convexity: 
            (\forall z \in \RR^n)\;  
            \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 \le h(z) - h(\tilde x) - \langle w,  z - \tilde x\rangle. 
        This means for all $z \in \RR^n$: 
            &\frac{B + \epsilon}{2}\Vert \tilde x - z \Vert^2 
            &\le 
            g(z) + \langle \nabla f(x), z\rangle + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \left(
                g(\tilde x) + 
                \langle \nabla f(x), \tilde x\rangle
                + 
                \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                \\ &\quad 
                - \langle w, z - \tilde x\rangle
                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                - \langle w, z - \tilde x\rangle
            \\&\quad 
                + \langle \nabla f(x), z - x + x -\tilde x\rangle
            &\underset{(1)}{=} 
                + \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
                - \langle w, z - \tilde x\rangle
                &\quad 
                - D_f(z, x) + f(z)
                + D_f(\tilde x, x) - f(\tilde x)
                - \langle w, z - \tilde x\rangle
            + 
                \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
                \\ &\quad 
                + \left(
                    D_f(\tilde x, x)
                    - \frac{B + \epsilon}{2}\Vert \tilde x - x\Vert^2
            \frac{B + \epsilon}{2}\Vert z - x\Vert^2 - D_f(z, x)
            + \left(
                \frac{B + \epsilon}{2}\Vert z - x\Vert^2
                - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            &\le
            F(z) - F(\tilde x) + \Vert w \Vert\Vert z - \tilde x\Vert
            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            &\underset{(3)}{\le}
            + \epsilon\Vert x - \tilde x\Vert\Vert z - \tilde x\Vert
            + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2. 
        At (1), we used: 
            & \langle \nabla f(x), z - x\rangle
            - \langle \nabla f(x), \tilde x - x\rangle
            - D_f(z, x) + f(z) - f(x)
            + D_f(\tilde x, x) - f(\tilde x) + f(x)
            &= f(z) + f(\tilde x) - D_f(z, x) + D_f(\tilde x , x). 
        At (2), we had $f$ convex as the assumption, hence $D_f(z, x) \le 0$. 
        We also had the assumption that $B$ makes $D_f(\tilde x, x) \le \frac{B}{2}\Vert \tilde x - x\Vert^2$, this simplies the third term from the previous line into $- \frac{\epsilon}{2}\Vert x - \tilde x\Vert^2$. 
        At (3), we applied the assumed inequality $\Vert w\Vert \le \epsilon \Vert x - \tilde x\Vert \Vert z - \tilde x\Vert$. 
        Continuing: 
            0 &\le
                F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
                - \frac{B + \epsilon}{2}\Vert z - \tilde x\Vert^2 
            + \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2
            &\underset{(4)}{=} 
            F(z) - F(\tilde x) + \frac{B + \epsilon}{2}\Vert z - x\Vert^2
            - \frac{B}{2}\Vert z - \tilde x\Vert^2. 
        At (4), we use some algebra: 

@@

            \epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2

@@

            &=\epsilon \Vert \tilde x - x\Vert \Vert z - \tilde x\Vert
            - \frac{\epsilon}{2}\Vert \tilde x - x\Vert^2 - \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2
            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2

@@

            - \epsilon(\Vert x - \tilde x\Vert - \Vert z -\tilde x\Vert)^2 
            + \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2 

@@

            &\le \frac{\epsilon}{2}\Vert z - \tilde x\Vert^2. 

@@

@@

    \subsection{The accelerated proximal gradient algorithm}
        \begin{definition}[accelerated inexact proximal gradient algorithm]\label{def:inxt-apg}
            Let 

@@

                \item $(\alpha_k)_{k \ge 0}$ be a sequence in $(0, 1]$. 
                \item Let $(B_k)_{k \ge 0}$ be a non-negative sequence. 
                \item Let $(F, f, g, L)$ be given by Assumption \ref{ass:smooth-nsmooth-sum}. 
                \item Let $(\epsilon_k)$ be a non-negative sequence that is the error schedule. 

@@

            Initialize with any $(x_{-1}, v_{-1})$. 
            For these given parameters, an algorithm is a type of accelerated proximal gradient if it generates $(y_k, x_k, v_k)_{k \ge 0}$ such that
            for $k\ge 0$: 

@@

                & y_{k} = \alpha_{k} v_{k - 1} + (1 - \alpha_{k}) x_{k - 1},
                & x_k \in T_{B_k + \epsilon_k}^{(\epsilon_k)}y_k: D_f(x, \tilde x) \le (1/2)\Vert x - \tilde x\Vert^2, 
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}).

@@

\section{convergence rates results}
    We will now show that Algorithms satisfying Definition \ref{def:inxt-apg} has desirable convergence rate. 
    \begin{assumption}[convergence assumptions]\label{ass:apg-cnvg}
        Let $(F, f, g, L)$ satisfies Assumption \ref{ass:smooth-nsmooth-sum} and in addition assume that $F$ admits a set of non-empty minimizers $X^+$. 
    \begin{lemma}[inexact one step convergence claim]\;\label{lemma:inxt-apg-onestep}\\
        Let $(F, f, g, L, X^+)$ satisfies Assumption \ref{ass:apg-cnvg}. 
        Suppose that an algorithm satisfies optimizes the given $F =f + g$ also satisfying Definition \ref{def:inxt-apg}.
        Then for the generated iterates $(y_k, x_k, v_k)_{k \ge 0}$, it has for all $k \ge 1$: 

@@

            &F(\bar x) - F(x_k)  - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2

@@

            &\le 
            \max\left(
                1 - \alpha_k, 
                \frac{\alpha_k(B_k + \epsilon_k)}{\alpha_{k -1}^2B_{k - 1}}
                F(x_{k - 1}) - F(\bar x) 
                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \right). 

@@

        Let $\bar x \in X^+$, making it a minimizer of $F$. 
        Define $z_k := \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
        It can be verified that:
        \begin{align}\begin{split}
            z_k - x_k &= \alpha_k(\bar x - v_k),

@@

            z_k - y_k &= \alpha_k(\bar x - v_{k - 1}).     
        \end{split}\tag{a}\label{lemma:inxt-apg-onestep-a}
        Because from Definition \ref{def:inxt-apg} it has for all $k \ge 1$: 
            z_k - x_k &= 
            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
            &= \alpha_kx^+ + (x_{k - 1} - x_k) - \alpha_kx_{k - 1}
            &= \alpha_k \bar x - \alpha_k v_k, 
            z_k - y_k &= 
            \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
            &= \alpha_k \bar x - \alpha_k v_{k - 1}. 
        For all $k \ge 0$, apply Theorem \ref{thm:inxt-pg-ineq} with $z = z_k, \tilde x = x_k, x = y_k, \epsilon = \epsilon_k, B = B_k$: 
            0 &\le 
            (F(z_k) - F(x_k) ) +
                \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
                - \frac{B_k}{2}\Vert z_k - x_k\Vert^2

@@

            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
            + 
                \frac{B_k + \epsilon_k}{2}\Vert z_k - y_k\Vert^2
                - \frac{B_k}{2}\Vert z_k - x_k\Vert^2

@@

            &\underset{\eqref{lemma:inxt-apg-onestep-a}}{=} 
            (\alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k))
                \\ &\quad 
                + \left(
                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                    - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2

@@

            F(\bar x) - F(x_k)
            + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                \\ &\quad 
                + \left(
                    \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2
                    - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2

@@

@@

            F(\bar x) - F(x_k) 
            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\ &\quad 
                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{2}\Vert \bar x - v_{k - 1} \Vert^2

@@

            &= F(\bar x) - F(x_k) 
            - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
                \\ &\quad
                + (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x))
                + \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}\frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2

@@

            F(\bar x) - F(x_k) - \frac{B_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2
            \\ &\quad 
            + \max\left(
                1 - \alpha_k, 
                \frac{(B_k + \epsilon_k)\alpha_k^2}{\alpha_{k - 1}^2B_{k - 1}}

@@

                F(x_{k - 1}) - F(\bar x) 
                + \frac{\alpha_{k - 1}^2B_{k - 1}}{2}\Vert \bar x - v_{k - 1} \Vert^2
            \right). 

@@

        At (1) we used convexity of $f$ which is assumed and it makes $f(z_k) \le \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1})$ because $\alpha_k \in (0, 1]$ from Definition \ref{def:inxt-apg}. 
    As a prelude, to derive the convergence rate we unroll the recurrence relation proved in the above lemma.
    It remains to create convergence criterions of the error relative sequence $\epsilon_k$ such that the original optimal convergence rate of $\mathcal O(1/k^2)$ the sequence remains unaffected. 
    Let the sequence $(B_k)_{k \ge 0}$ be given by **Definition 2**. 
    We suggest the following descriptors using another sequence $\rho_k$ given by for all $k \ge 1$: 
        \rho_k &= \frac{B_k + \epsilon_k}{B_{k - 1}}\frac{B_{k - 1}}{B_k}.
    This means the following: 
        \max\left(
            1 - \alpha_k, 
            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
        \max\left(
            \sim, 
            \rho_k\frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        &\le \max(1, \rho_k)\max\left(
            \sim, 
            \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        \right). 
    If we consider $\rho_k \le (1 + 2/k^2)$, it has the ability to make
        \prod_{k = 1}^{n} 
        \max \left(
            1 - \alpha_k, 
            \frac{\alpha_k^2(B_k + \epsilon_k)}{\alpha_{k - 1}^2B_{k - 1}}
        &\le 
        \prod_{k = 1}^{n} 
        \max(1, \rho_k)
        \prod_{i = 1}^{n}
            \max\left(
                1 - \alpha_k, 
                \frac{B_k\alpha_k^2}{B_{k - 1}\alpha_{k - 1}^2}
        &\le \prod_{k = 1}^n
            1 + \frac{2}{k^2}
        (\sim)
        &\le 2 (\sim). 

    The following lemma will seal the case for the other remaining big product above.

\bibliographystyle{siam}

\bibliography{references/Books.bib}

\end{document}

>>>>

% NOTATIONS FOR THIS PAPER 
\DeclareMathOperator{\dist}{\mathop{dist}}
\DeclareMathOperator{\rng}{\mathop{rng}}

\title{{\fontfamily{ptm}\selectfont Inexect Accelerated Proximal Gradient }}

@@

% TITLE, ABSTRACT ==============================================================
\date{\today}
\maketitle
\todoinline{This paper is currently in draft mode. Check source to change options. }
\begin{abstract} 
    \noindent
    This is still a draft. \cite{zhang_robust_2022}. 
\end{abstract}
\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 47H05, 52A41, 90C25; Secondary 15A09, 26A51, 26B25, 26E60, 47H09, 47A63.
\noindent{\bfseries Keywords:}

\section{Introduction}
    \textbf{Notations.}
    Let $g: \RR^n \rightarrow\overline \RR$, we denote $g^\star$ to be the Fenchel conjugate. 
    $I: \RR^n \rightarrow \RR^n$ denotes the identity operator.
    For a multivalued mapping $T: \RR^n \rightarrow 2^{\RR^n}$, $\gra T$ denotes the graph of the operator, defined as $\{(x, y)\in \RR^n \times \RR^n : y \in Tx\}$. 
    \subsection{Epsilon subgradient and inexact proximal point}
        \begin{definition}[epsilon subgradient]\label{def:esp-subgrad}
            Let $g: \RR^n \rightarrow \overline \RR$ be proper, lsc. 
            Then the $\epsilon$-subgradient of $g$ at some $\bar x \in \dom g$ is given by: 
            \begin{aligned}
                \partial g_\epsilon(\bar  x) := 
                \left\lbrace
                    v \in \RR^n \left| \; 
                        \langle v, x - \bar  x\rangle \le 
                        g(x) - g(\bar x) + \epsilon \;\forall x \in \RR^n
                    \right. 
                \right\rbrace.
            \end{aligned}
            When $\bar x \not \in \dom g$, it has $\partial g_\epsilon(\bar x) = \emptyset$. 

@@

        \begin{remark}
            $\partial_\epsilon g$ is a multivalued operator and, it's not monotone, unless $\epsilon = 0$, which makes it equivalent to French subgradient $\partial g$. 
        \end{remark}
        If we assume lsc, proper and convex $g$, we will now introduce results in the literatures that we will use. 
        \begin{fact}[epsilon Fenchel inequality]\label{fact:esp-fenchel-ineq}
            Let $\epsilon \ge 0$, then:

@@

                x^* \in \partial_\epsilon f(\bar x)\iff f^\star(x^*) + f(\bar x) \le \langle x^*, \bar x\rangle + \epsilon \implies \bar x \in \partial_\epsilon f^\star(x^*).
            They are all equivalent if $f^{\star\star}(\bar x) = f(\bar x)$. 
        \end{fact}
        \begin{remark}
            The above fact is taken from Zalinascu \cite[Theorem 2.4.2]{zalinescu_convex_2002}. 
        \end{remark}
        % \begin{fact}[strong epsilon subgradient sum rule]\label{fact:esp-subgrad-sum-rule}
        %     Take both $f, g: \RR^n\rightarrow \overline \RR$. 
        %     Let $\epsilon \ge 0$. 
        %     Then the epsilon subgradient sum rule states that 
        %     \begin{align*}
        %         \partial_\epsilon[f + g](\bar x) = 
        %         \bigcup \left\lbrace
        %             \partial_{\epsilon_1} f(\bar x) + 
        %             \partial_{\epsilon_2} g(\bar x) \left|\; 
        %                 \min(\epsilon_1, \epsilon_2) \ge 0\wedge 
        %                 \epsilon_1 + \epsilon_2 = \epsilon
        %             \right.
        %         \right\rbrace
        %     \end{align*}
        %     Under the scenario that: $\reli\dom f \cap \reli\dom g \neq \emptyset$. 
        % \end{fact}
        % \begin{remark}
        %     The above is taken from Morduchovich, Mau Nam \cite[Theorem 5.19]{mordukhovich_convex_2022}. 
        % \end{remark}
        We will now define inexact proximal point based on epsilon subgradient
        \begin{definition}[inexact proximal point]
            For all $x \in \RR^n, \epsilon \ge 0, \lambda > 0$, $\tilde x$ is an inexact evaluation of proximal point at $x$, if and only if it satisfies: 
                \lambda^{-1}(x - \tilde x) \in \partial_{\epsilon} g(\tilde x). 
            We denote it by $\tilde x \approx_\epsilon \hprox_{\lambda g}(x)$. 
        \begin{remark}
            This definition is nothing new, for example see Villa et al. \cite[Definition 2.1]{villa_accelerated_2013}
        \end{remark}
        \begin{fact}[the resolvant identity]\label{fact:resv-identity}
            Let $T: \RR^n \rightarrow 2^{\RR^n}$, then it has: 
                (I + T)^{-1} = (I - (I + T^{-1})^{-1}).
        \end{fact}
        \begin{theorem}[inexact Moreau decomposition]
            Let $g: \RR^n \rightarrow \overline \RR$ be a closed, convex and proper function. 
            It has the equivalence
                \tilde y \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)
                \iff 
                y - \lambda \tilde y \approx_\epsilon \hprox_{\lambda g}(y). 

@@

            Consider $\tilde y \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)$, then it has: 

@@

                \tilde y 
                \in (I + \lambda^{-1}\partial_\epsilon g^\star)^{-1}(\lambda^{-1}y)

@@

                \iff &
                (\lambda^{-1}y, \tilde y)\in 
                \gra(I + \lambda^{-1}\partial_\epsilon g^\star)^{-1}

@@

                \underset{(1)}{\iff} &
                (\lambda^{-1}y, \tilde y)\in 
                \gra(I - (I + \partial_\epsilon g\circ(\lambda I))^{-1})

@@

                \iff &
                (\lambda^{-1}y, \lambda^{-1}y - \tilde y)\in 
                \gra(I + \partial_\epsilon g\circ(\lambda I))^{-1}
                \iff &
                (\lambda^{-1}y - \tilde y, \lambda^{-1}y)\in 
                \gra(I + \partial_\epsilon g\circ(\lambda I))
                \iff &
                (y - \lambda\tilde y, \lambda^{-1}y)\in 
                \gra(\lambda^{-1}I + \partial_\epsilon g)
                \iff &
                (y - \lambda\tilde y, y)\in 
                \gra(I + \lambda\partial_\epsilon g)
                \iff& 
                y - \lambda \tilde y \in 
                (I + \lambda \partial_\epsilon g)^{-1}y
                \iff& 
                y - \lambda \tilde y \approx_\epsilon \hprox_{\lambda g}(y). 

@@

            At (1) we can use Fact \ref{fact:resv-identity}, and it has $(\lambda^{-1}\partial_\epsilon g^\star)^{-1} = \partial_\epsilon g\circ(\lambda I)$ by Fact \ref{fact:esp-fenchel-ineq} and the assumption that $g$ is closed, convex and proper. 

@@

    \subsection{Inexact proximal gradient inequality}
        \begin{assumption}[for inexact proximal gradient]\label{ass:for-inxt-pg-ineq}
            The assumption is about $(f, g, L)$. 
            We assume that 

@@

                \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz function. 
                \item $g: \RR^n \rightarrow \overline\RR$ is a convex, proper, and lsc function which we do not have its exact proximal operator. 

@@

        We develop the theory based on the use of epsilon subgradient as in Definition \ref{def:esp-subgrad}. 
        \begin{definition}[inexact proximal gradient]\label{def:inxt-pg}
            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}. 
            Then, $\tilde x \approx_\epsilon T_B(x)$ is an inexact proximal gradient if it satisfies variational inequality: 

@@

                \mathbf 0 \in \nabla f(x) + B(x - \tilde x) + \partial_{\epsilon} g(\tilde x). 

@@

        \begin{remark}
            We assumed that we can get exact evaluation of $\nabla f$ at any points $x \in \RR^n$. 
        \end{remark}
        \begin{lemma}[other representations of inexact proximal gradient]\;\\
            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq}.
            Let $\epsilon \ge 0, B \ge 0$, then for all $x \approx_\epsilon T_B(x)$, it has the following equivalent representations: 

@@

                & (x - B^{-1}\nabla f(x)) - \tilde x 
                \in B^{-1} \partial_\epsilon g(\tilde x)

@@

                \iff 
                & \tilde x \in (I + B^{-1}\partial_\epsilon g(\tilde x))^{-1}
                (x - B^{-1}\nabla f(x))
                \iff 
                & x \approx_\epsilon \hprox_{B^{-1} g}
                \left(x - B^{-1}\nabla f(x)\right)

@@

            It's direct. 
        \begin{theorem}[inexact over-regularized proximal gradient inequality]\;\label{thm:inxt-pg-ineq}\\
            Let $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-pg-ineq} . 
            Consider $\tilde x \approx_\epsilon T_{B + \beta}(x)$. 
            If in addition, it satisfies $D_f(\tilde x, x) \le B/2\Vert x - \tilde x\Vert^2$, then it has $\forall z \in \RR^n$: 
                - \epsilon &\le 
                + \frac{B + \beta}{2}\Vert x - z\Vert^2
                - \frac{B + \beta}{2}\Vert z - \tilde x\Vert^2
                - \frac{\beta}{2}\Vert \tilde x - x\Vert^2. 
            By Definition \ref{def:inxt-pg} write the variational inequality that describes $\tilde x \approx_\epsilon T_B(x)$, and the definition of epsilon subgradient (Definition \ref{def:esp-subgrad}) it has for all $z \in \RR^n$: 
                - \epsilon &\le 
                g(z) - g(\tilde x) - \langle (B + \beta)(\tilde x - x) - \nabla f(x), z - \tilde x\rangle

@@

                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
                + \langle \nabla f(x), z - \tilde x\rangle

@@

                g(z) + f(z) - g(\tilde x) - f(\tilde x)
                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
                - D_f(z, x) + D_f(\tilde x, x)

@@

                - (B + \beta)\langle \tilde x - x, z - \tilde x\rangle
                + \frac{B}{2}\Vert \tilde x - x\Vert^2

@@

                F(z) - F(\tilde x) + \frac{B + \beta}{2}\left(
                    \Vert x - z\Vert^2
                    - \Vert \tilde x - x\Vert^2
                    - \Vert z - \tilde x\Vert^2

@@

                + \frac{B}{2}\Vert \tilde x - x\Vert^2

@@

                + \frac{B + \beta}{2}\Vert x - z\Vert^2
                - \frac{B + \beta}{2}\Vert z - \tilde x\Vert^2
                - \frac{\beta}{2}\Vert \tilde x - x\Vert^2. 
            At (1), we used considered the following: 
                \langle \nabla f(x), z - x\rangle &= \langle \nabla f(x), z - x + x - \tilde x\rangle

@@

                &= \langle \nabla f(x), z - x\rangle + \langle \nabla f(x), x - \tilde x\rangle

@@

                &= -D_f(z, x) + f(z) - f(x) + D_f(\tilde x, x) - f(\tilde x) + f(x)
                &= -D_f(z, x) + f(z) + D_f(\tilde x, x) - f(\tilde x). 
            At (2), we used the fact that $f$ is convex hence $- D_f(z, x) \le 0$ always, and in the statement hypothesis we assumed that $B$ has $D_f(\tilde x, x) \le B/2\Vert \tilde x - x\Vert^2$. 
    \subsection{optimizing the inexact proximal point problem}
        In this section we will show an optimization problem that allows us to solve for some $\tilde x \approx_\epsilon \hprox_{\lambda g}(z)$. 
        Most of these results are from the literature. 
        To start, we must assume the following about a function $g: \RR^n \rightarrow \overline \RR$, with $g$ closed, convex and proper. 
        \begin{assumption}[for inexact proximal operator]\;\label{ass:for-inxt-prox}\\
            This assumption is about $(g, \omega, A)$. 
            Let $m \in \N, n \in \RR^n$, we assume that 
                \item $A\in \RR^{m \times n}$ is a matrix. 
                \item $\omega: \RR^n \rightarrow \overline \RR$ is a closed and convex function such that it admits proximal operator $\hprox_{\lambda\omega}$ and, its conjugate $\omega^\star$ is known. 
                \item $g := \omega(Ax)$ such that $\rng A \cap \reli\dom g \neq\emptyset$. 
        Now, we are ready to discuss how to choose $\tilde x \approx_\epsilon \hprox_{\lambda g}(x)$. 
        Fix $y \in \RR^n, \lambda > 0$, we are ultimately interested in minimizing: 
        \begin{align}
            \Phi_\lambda(u) &:= \omega(Au) + \frac{1}{2\lambda} \Vert u - y\Vert^2
        This problem admits dual objective in $\RR^m$: 
        \begin{align}
            \Psi_\lambda(v) &:=
            \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2
            + \omega^\star(v) - \frac{1}{2\lambda}\Vert y\Vert^2. 
        We define the duality gap
        \begin{align}
            \mathbf G_\lambda(u, v) &:= \Phi_\lambda(u) + \Psi_\lambda(v). 
        If strong duality holds, it exists $(\hat u, \hat v)$ such that we have the following: 
            \mathbf G_\lambda(\hat u, \hat v) = 0 = \min_{u} \Phi_\lambda(u) + \min_v \Psi_\lambda(v)
        The following theorem quantifies a sufficient conditions for $\tilde x \approx_\epsilon \hprox_{\lambda g}(x)$. 
        The theorem below is from \cite[Proposition 2.2]{villa_accelerated_2013}. 
        \begin{theorem}[primal translate to dual]\label{thm:primal-dual-trans}
            Let $\epsilon \ge 0$, $g:\RR^n \rightarrow \overline \RR$ be convex, proper and closed then 

@@

                    \forall z \approx_\epsilon \hprox_{\lambda g}(y) 
                \right)(\exists v \in \dom \omega^\star): z = y - \lambda B^\top v. 

@@

        The theorem is from Villa et al. \cite[Proposition 2.3]{villa_accelerated_2013}
        \begin{theorem}[duality gap of inexact proximal problem]\label{thm:dlty-gap-inxt-pp}
            For all $\epsilon \ge 0$, $v \in \RR^n$. 
            Consider conditions 
                \item $\mathbf G_\lambda(y - \lambda B^\top v, v) \le \epsilon$. 
                \item $B^\top v \approx_\epsilon \hprox_{\lambda^{-1}g^\star}(\lambda^{-1}y)$. 
                \item $y - \lambda B^\top v \approx_{\epsilon} \hprox_{\lambda g}(y)$. 
            They have $(a)\implies (b) \iff (c)$. 
            If in addition $\omega^\star(v) = g^\star(B^\top v)$, then all three conditions are equivalent. 
        Next, let's explore some options for minimizing the duality gap of the proximal problem. 
        \todoinline{
            STILL WRITING AND NOT FINISHED YET! 
        }

    \subsection{Literature reviews}
\bibliographystyle{siam}
\bibliography{references/refs.bib}
\end{document}
